### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@f70eeaff425c8fea2fde89c44e86ab3146ebb47f 🚀

Interactions between plants and pollinators form networks of
interactions, which structure the ``architecture of biodiversity''
(\textbf{Jordano2007?}). The persistence, functioning, and stability of
ecosystems emerge from these interactions, but antropogenic change
threatens to unravel and ``rewire'' these networks
(\textbf{CaraDonna2017IntRew?}). Plant-pollinator networks face two
possible forms of rewiring in response to anthropogenic environmental
change: spatial and temporal.\\
Spatially, range shifts could cause interacting species to no longer
overlap in space, and shifts in phenology could cause interacting
species to no longer overlap in time.

This chapter uses several years of data on bumblebee-flower phenology
and interactions across several field site, each consisting of several
plots across an elevational gradient, combined with spatial records of
species occurrence via GBIF to forecast this uncoupling.

Addresses the EBV to forecast of EBV element of the flow from data to
mitigation in fig.~\ref{fig:thesis}.

@@

The data for this chapter is derived from multiple souces and can be
split into three categories. (1) Field data from three different
locations across Colorado. All field sites have multiple plots across an
elevational gradient.

System description: lots of data on \emph{Bombus} (bumblebees) and
wildflowers. Three different sites, (7/7/3) years each, each covering an
elevational gradient.

@@

The issue is that we don't really know what interactions are like now.
So we also need to predict interactions as they exist \emph{in the
present} as the data we have and temporally sparse and likely to contain
many interaction ``false-negatives'' (Strydom \emph{et al.} 2021).

@@

We propose various landscape modifications which alter the cover of a
landscape, represented as a raster (fig.~6, left). We then compute a new
resistance surface based on the proposed landscape modification, and
based on the values of resistance to dispersal between each location we
simulate spatially-explicit metapopulation dynamics model (Hanski \&
Ovaskainen 2000; Ovaskainen \emph{et al.} 2002) to estimate a
distribution of time until extinction for each landscape modification
(fig.~6, right).

@@

\begin{itemize}
\item
  land cover -\textgreater{} resistance -\textgreater{} extinction time
\item
  brief overview of simulated annealing
\item
  describe how you build the proposal function
\item
  optimize landscape optimization
\end{itemize}

@@

This chapter consists of a collection of modules in the Julia language
for different aspects of community ecology, including most of the code
used for the preceding chapters.

Indeed \texttt{MetacommunityDynamics.jl} is the center of this, but due
to the nature of the Julia language, it is interoperable with serveral
existing packages.

\texttt{EcoJulia} organization, including several which I have
contributed to enable interoperability with MCD.jl.

A diagram showing the relation between these packages is shown in
fig.~\ref{fig:software}.

\begin{figure}
\hypertarget{fig:software}{%
\centering
\includegraphics{./figures/ch4.png}
\caption{todo}\label{fig:software}
}
\end{figure}

>>>>

Interactions between plants and pollinators form networks of
interactions, which structure the ``architecture of biodiversity''
(\textbf{Jordano2007?}). The functioning and stability of ecosystems
emerge from these interactions, but antropogenic change threatens to
unravel and ``rewire'' these networks (\textbf{CaraDonna2017IntRew?}),
threating the persistence of these systems. Plant-pollinator networks
face two possible forms of rewiring in response to anthropogenic
environmental change: spatial and temporal.\\
Spatially, range shifts could cause interacting species to no longer
overlap in space, and shifts in phenology could cause interacting
species to no longer overlap in time.

This chapter uses several years of data on bumblebee-flower phenology
and interactions across several field sites, each consisting of several
plots across an elevational gradient, combined with spatial records of
species occurrence via GBIF to forecast this uncoupling. This addresses
the EBV to forecast of EBV element of the flow from data to mitigation
in fig.~\ref{fig:thesis} (left).

@@

The data for this chapter is derived from multiple souces and can be
split into four categories. (1) Field data from three different field
sites across Colorado, each with multiple plots across an elevational
gradient, for seven, seven, and three years resptively. This data was
collected by Paul CaraDonna and Jane Oglevie (from the Rocky Mountain
Biological Laboratory) and Julian Resasco (CU Boulder). (2) GBIF spatial
occurrence records of each of these species across Colorado, including a
metaweb of interactions across all of Colroado taken from GBIF. (3)
Remotely sensed data consisting of current and forecasting bioclimatic
variables from CHELSA. (4) Phylogeny derived from NCBI GenBank barcodes
for mitochondrial COI (bumblebees) and chloroplast rbcL (flowers).

@@

As the data we have is spatially sparse and likely to contain many
interaction ``false-negatives'' (Strydom \emph{et al.} 2021), we beign
by predicting a metaweb of interactions as they exist \emph{in the
present}.

@@

\begin{figure}
\hypertarget{fig:ch3}{%
\centering
\includegraphics{./figures/ch3.png}
\caption{fig}\label{fig:ch3}
}
\end{figure}

@@

We propose various landscape modifications which alter the cover of a
landscape, represented as a raster. We then compute a new resistance
surface based on the proposed landscape modification, and based on the
values of resistance to dispersal between each location we simulate
spatially-explicit metapopulation dynamics model (Hanski \& Ovaskainen
2000; Ovaskainen \emph{et al.} 2002) to estimate a distribution of time
until extinction for each landscape modification.

\begin{itemize}
\tightlist
\item
  brief overview of simulated annealing
\item
  describe how you build the proposal function
\item
  optimize landscape optimization
\end{itemize}

@@

This chapter consists of a collection of modules in the Julia language
for different aspects of community ecology, including most of the code
used for the preceding chapters. Indeed
\texttt{MetacommunityDynamics.jl} (MCD.jl) is the epicenter of this set
of tools, but due to the nature of the Julia language, MCD.jl is
interoperable with serveral existing packages within the
\texttt{EcoJulia} organization, including several to which I have
contributed. A diagram showing the relation between these packages is
shown in fig.~\ref{fig:software}.

\begin{figure}
\hypertarget{fig:software}{%
\centering
\includegraphics{./figures/ch4.png}
\caption{The structure of the software libraries used as part of
MCD.jl}\label{fig:software}
}
\end{figure}
